### 2018-02-22 paper/algorithm.tex
updated text according to figure

When Alice wants to transfer a file to Bob, she will find which devices have the 
file (from \(F_i\)), then predict when any of those devices will be available 
(from \(A_i\)).
Then she will construct a probabilistic onion route with her devices as the 
destinations.
She will encrypt this route for Bob and transfer it to him, who now can use the 
onion route to fetch the file.

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=0.8\columnwidth]{figures/schema.pdf}
\caption{\label{fig:pipeline}Pipeline of the steps undergone by Alfred when he shares a file from his laptop L with Beth.}
\end{figure}

Figure~\ref{fig:pipeline} depicts the process of a file exchange from Alfred to Beth.
The file $f$ is initially located on Alfred's laptop $L$, which is potentially offline for now.
Firstly, Alfred and Beth need to exchange encryption keys and the key $ID_f$ referencing the file on the DHT.
They do so \emph{out-of-band}, that is using another channel than the one presented here (e.g. bluetooth, email...).

Then, Alfred queries the DHT for devices that will most likely be online at the same time as his laptop $L$.
To this end, Alfred uses his knowledge on his devices connection patterns $A_i$, along with the DHT's public information on devices connections.
Once Alfred and the DHT agreed upon a set of peers $(M_1, M_2, M_3)$, their address is put in the DHT at the key $ID_f$ referencing the file of interest.

At the third step, Alfred's laptop $L$ becomes available. 
Informed of the ongoing file exchange by Alfred's Device Swarm Protocol, $L$ fetches the addresses of $M_1, M_2$ and $M_3$ on the DHT using the key $ID_f$.
These peers will serve as middle-men: $L$ sends them redundant chunks of $f$ through an onion route (thus remaining anonymous), for Beth to fetch them later.

In the last forth step, Beth fetches the file $f$ using any of her devices.
To do so, she uses the key $ID_f$ to learn the addresses of $M_1, M_2$ and $M_3$.
Then, she fetches parts of $f$ from the online middle-men through an onion route.
Given that $L$ sent redundant chunks to the middle-men, Beth will not need every middle-man to be connected to fetch the whole file.
Once Beth has completed the download, the key $ID_f$ is flushed on the DHT.

% When Alfred and Beth want to exchange a file owned by Alfred, they first need to exchange their

% When Alfred wants to transfer a file to Beth, she will find which devices have the 
% file (from \(F_i\)), then predict when any of those devices will be available 
% (from \(A_i\)).
% Then she will construct a probabilistic onion route with her devices as the 
% destinations.
% She will encrypt this route for Beth and transfer it to him, who now can use the 
% onion route to fetch the file.
